Cross-Validation Default

### 2023-07-03 minos/validation/cross_validation_default.Rmd
Added lots of secondary variables to cross_validation_default.Rmd

## Housing Quality

@@

## Neighbourhood Safety

@@

## Loneliness

@@

## Nutrition Quality

@@

## Tobacco Use

@@

>>>>

# Housing Quality

@@

# Neighbourhood Safety

@@

# Loneliness

@@

# Nutrition Quality

@@

# Tobacco Use

@@

# Financial Situation

```{r}
fsit.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'financial_situation')

cv_ordinal_plots(pivoted.df = fsit.pivoted, 
                 var = 'financial_situation',
                 save = FALSE)

rm(fsit.pivoted)
```

# Heating

```{r}
heat.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'heating')

cv_ordinal_plots(pivoted.df = heat.pivoted, 
                 var = 'heating',
                 save = FALSE)
```

# SECONDARY VARS

## Marital Status

```{r}
mstat.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'marital_status')

cv_ordinal_plots(pivoted.df = mstat.pivoted, 
                 var = 'marital_status',
                 save = FALSE)

rm(mstat.pivoted)
```

## hhsize

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hhsize')

multi_year_boxplots(raw, cv, 'hhsize')
```

## housing tenure

```{r}
tenure.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'housing_tenure')

cv_ordinal_plots(pivoted.df = tenure.pivoted, 
                 var = 'housing_tenure',
                 save = FALSE)

rm(tenure.pivoted)
```

## Ethnicity

```{r}
ethnic.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'ethnicity')

cv_ordinal_plots(pivoted.df = ethnic.pivoted, 
                 var = 'ethnicity',
                 save = FALSE)

ethnic.piv.nowhite <- filter(ethnic.pivoted, ethnicity != 'WBI')

cv_ordinal_plots(pivoted.df = ethnic.piv.nowhite, 
                 var = 'ethnicity',
                 save = FALSE)

rm(ethnic.pivoted, ethnic.piv.nowhite)
```
